%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Search Engine Optimization Expert}
{Marweb Marketing Agency}
{Remote}
{Aug. 2022 - Present}
{
\begin{cvitems}
\item {Rebuilt SEO strategy around high-intent, revenue-driving keywords, shifting focus from traffic volume to business outcomes and significantly improving lead quality and sales impact.}
\item {Scaled organic visibility across multiple industries by combining Technical SEO, advanced on-page optimization, and site architecture improvements, resulting in higher CTR and consistently stronger conversion performance.}
\item {Designed SEO architectures that maximized crawl efficiency, internal linking, and site structure, reducing dependence on link-building while achieving competitive rankings with lower external costs.}
\item {Replaced paid acquisition with high-converting organic channels, reducing Google Ads spend by up to 50\% for multiple customers while maintaining or increasing total conversions.}
\item {Positioned SEO and LLM-based discovery (AI-driven search and generative results) as primary acquisition channels, future-proofing client visibility beyond traditional search engines.}
\item {Built internal SEO automation tools in Python and Selenium for large-scale site analysis, doubling agency operational capacity, accelerating delivery, and minimizing human error with the same team size.}
\item {Delivered sustained growth in qualified traffic and conversion rates, directly lowering customer acquisition costs and increasing overall marketing ROI.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Search Engine Optimization Specialist}
{EDUKIWI / Clientipeviata}
{Remote}
{Jul. 2021 - Sep. 2022}
{
\begin{cvitems}
\item {Advanced from Junior SEO to leading junior team members, structuring workflows with developers and copywriters to increase delivery capacity across multiple client accounts.}
\item {Standardized SEO execution across 20+ concurrent projects by building internal procedures based on official Google documentation and live campaign data, reducing errors and increasing consistency of results.}
\item {Created onboarding and training frameworks that enabled new hires to become fully independent within one month, cutting mentoring time and significantly improving team throughput.}
\item {Owned client relationships end-to-end, working directly with business owners to define objectives, align SEO with revenue goals, and present measurable results in monthly performance reviews.}
\item {Directed technical SEO, content strategy, and link-building in cross-functional teams, consistently increasing relevant organic traffic and the quality of inbound leads.}
\item {For long-term customers (12+ months), built full-funnel SEO for both lead generation and eCommerce, pre-qualifying traffic and increasing conversion rates from under 10\% to over 25\%.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Accountant}
{Fratelli Galați}
{Galați, Romania}
{Jan. 2018 - Jul. 2021}
{
\begin{cvitems}
\item {Owned full-cycle accounting for a multi-location hospitality business, ensuring accurate bookkeeping, payroll, supplier payments, and financial reporting to support daily operations and management decisions.}
\item {Prepared financial statements up to balance sheet level and maintained full regulatory compliance, achieving zero audit issues and flawless ANAF reporting.}
\item {Managed cash flow, vendor settlements, and internal financial controls, improving financial visibility and operational stability across the business.}
\end{cvitems}
}

\end{cventries}
